---
title: "Prop_surf_precip"
author: "Yusuf Jameel"
date: "9/9/2019"
output: html_document
---



```{r include=FALSE}
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(dplyr)
library(mvtnorm)
library(lubridate)
library(MASS)
setwd("/Users/yusufjameel/Dropbox/Arsenic_MIT/data_prior/isotope_analysis/data")
source("./Functions/As_mM_to_ppb.R")
source("./Functions/As_ppb_to_mM.R")
source("./Functions/Categorize_As_many_levels.R")
source("./Functions/Categorize_depths.R")
source("./Functions/Generate_gridded_data.R")
source("./Functions/Make_maps.R")
source("./Functions/load_powell_database.R")
source("./Functions/Make_raster_maps.R")
source("./Functions/Make_tm_maps.R")
source("./Functions/Make_interactive_map_any.R")
source("./Functions/Make_interactive_map_Dex.R")
source("./Functions/Make_interactive_map_As_styling_bgs.R")
```

##Loading data from the database 

```{r}
Arsenic_db <- load_powell_database()
```

<br/>
###subsetting isotope data (including depth and study_ID as well) only for Bengal


```{r include =FALSE}
As_iso = subset(Arsenic_db, Arsenic_db$d18O__permil != "NA")
iso_data = subset(As_iso, As_iso$Country == "India" | As_iso$Country == "Bangladesh")
iso_Beng= data.frame(cbind(iso_data$Sample_ID, iso_data$Country, iso_data$Study_ID, iso_data$Water_Source, iso_data$Depth__m, iso_data$d18O__permil, iso_data$d2H__permil, iso_data$Long, iso_data$Lat))

colnames(iso_Beng) = c("Sample_ID", "Country", "Study_ID", "Water_Source","Depth_m", "d18O","d2H", "Long", "Lat")

iso_Beng$d18O = as.numeric(levels(iso_Beng$d18O))[iso_Beng$d18O]
iso_Beng$d2H = as.numeric(levels(iso_Beng$d2H))[iso_Beng$d2H]
iso_Beng$Long = as.numeric(levels(iso_Beng$Long))[iso_Beng$Long]
iso_Beng$Lat = as.numeric(levels(iso_Beng$Lat))[iso_Beng$Lat]
iso_Beng_gw = subset(iso_Beng, iso_Beng$Water_Source == "GW")
iso_Beng_sw = subset(iso_Beng, iso_Beng$Water_Source == "SW")
iso_Beng_sw$Depth_m = 0


iso_Beng_precip = iso_Beng[which(iso_Beng$Water_Source == "PRECIP"),]
iso_Beng_precip$Date_sampled = NA
iso_Beng_precip$Rainfall_amount = NA
iso_Beng_precip$Month = NA

iso_Beng_precip = iso_Beng_precip[,c(1,6,7,4,10,3,11,5,2,9,8,12)]
names(iso_Beng_precip)[10] = "Latitude" 
names(iso_Beng_precip)[11] = "Longitude" 



Precip_isotope_other <-read.csv('Precip_isotopes2.csv', as.is = T)
Precip_isotope_other <-subset(Precip_isotope_other, Precip_isotope_other$Country %in% c("India", "Bangladesh"))
Precip_isotope_other <-subset(Precip_isotope_other, !(Precip_isotope_other$Sample_ID == "SHILLONG"))
Precip_isotope_other = Precip_isotope_other[,-12]

#########SPATIAL DATABASE

Precip_spatial_DB <-read.csv('Precip_bengal_spatial_DB.csv', as.is = T)
Precip_spatial_DB  <- Precip_spatial_DB[,c(1,14,15,16,13,21,2,3)]
Precip_spatial_DB = Precip_spatial_DB[-which(is.na(Precip_spatial_DB$d18O)),]
#aa = which(Precip_spatial_DB$d2H == 9999)
#Precip_spatial_DB  <- Precip_spatial_DB[-aa,]
Precip_spatial_DB$Water_Source ="Precip"
Precip_spatial_DB$Study_ID = "Spatial_DB"
#Precip_spatial_DB$Rainfall_amount = "NA"
Precip_spatial_DB$Depth_m = 0
Precip_spatial_DB$Country = "Bangladesh"
names(Precip_spatial_DB)[5] <- "Date_sampled"
names(Precip_spatial_DB)[1] <- "Sample_ID"
#Precip_spatial_DB$Month = month(ymd(Precip_spatial_DB$Date_sampled))
Precip_spatial_DB = Precip_spatial_DB[c(1,2,3,9,5,10,4,11,12,7,8,6)]


## Join all the precip data together
d18O_all =c(Precip_spatial_DB$d18O,Precip_isotope_other$d18O,iso_Beng_precip$d18O)
d2H_all = c(Precip_spatial_DB$d2H,Precip_isotope_other$d2H,iso_Beng_precip$d2H)
rain_amt_all = c(Precip_spatial_DB$Rainfall_amount,Precip_isotope_other$Rainfall_amount,iso_Beng_precip$Rainfall_amount)
Dex = d2H_all - 8*d18O_all

aa = which(rain_amt_all  > 0)
oxy_amount = rain_amt_all[aa]*d18O_all[aa]
oxy_amount_wt = sum(oxy_amount)/sum(rain_amt_all[aa])
hydro_amount = rain_amt_all[aa]*d2H_all[aa]
hydro_amount_wt = sum(hydro_amount)/sum(rain_amt_all[aa])

```


## LMWL for Bengal, Dhaka and Kolkata


```{r include = F}
LMWL_Bengal <- lm(d2H_all ~ d18O_all)

```

##### let's calculate the amount weighted mean and standard deviation
```{r}

### let's get standard deviation /variance^2

Rainfall_fraction = rain_amt_all/sum(rain_amt_all[aa])

var_hydro =sum(rain_amt_all[aa]*(d2H_all[aa] - hydro_amount_wt)^2)/(((length(aa)-1)*sum(rain_amt_all[aa]))/(length(aa)))
var_oxy =sum(rain_amt_all[aa]*(d18O_all[aa] - oxy_amount_wt)^2)/(((length(aa)-1)*sum(rain_amt_all[aa]))/(length(aa)))


c_oh = cor(d18O_all[aa],d2H_all[aa])*(var_hydro*var_oxy)^0.5
h_precip_mean = hydro_amount_wt 
o_precip_mean = oxy_amount_wt
kk = rmvnorm(5000, c(o_precip_mean,h_precip_mean), matrix(c(var_oxy, rep(c_oh,2), var_hydro),2,2))
plot(kk[,1], kk[,2])
abline(LMWL_Bengal$coefficients[1],LMWL_Bengal$coefficients[2], lwd = 1, lty= 2, col = "blue")
grid()

```

```{r}
bivn.kde <- kde2d(kk[,1], kk[,2], n = 500)
image(bivn.kde,  xlim = c(-17,4), ylim = c(-130,30), xlab = "d18O", ylab = "d2H")
#points(kk[,1], kk[,2], alpha = 0.8 )
grid()
contour(bivn.kde, add = TRUE, lwd = 0.5)
abline(LMWL_Bengal$coefficients[1],LMWL_Bengal$coefficients[2], lwd = 1, lty= 2, col = "blue")
title("weighted precip isotope distri")
##############
```

```{r}
sum(sum(Rainfall_fraction[which(d18O_all>= 0)], na.rm=T),
sum(Rainfall_fraction[which(d18O_all >= -2 & d18O_all < 0)], na.rm=T),
sum(Rainfall_fraction[c(which(d18O_all >= -4 & d18O_all < -2))], na.rm=T),
sum(Rainfall_fraction[c(which(d18O_all >= -6 & d18O_all < -4))], na.rm=T),
sum(Rainfall_fraction[c(which(d18O_all >= -8 & d18O_all < -6))], na.rm=T),
sum(Rainfall_fraction[c(which(d18O_all >= -10 & d18O_all < -8))], na.rm=T),
sum(Rainfall_fraction[c(which(d18O_all >= -12 & d18O_all < -10))], na.rm=T),
sum(Rainfall_fraction[c(which(d18O_all >= -14 & d18O_all < -12))], na.rm=T),
sum(Rainfall_fraction[which(d18O_all < -14)], na.rm=T))

rain_amt_group = c(sum(Rainfall_fraction[which(d18O_all>= 0)], na.rm=T),
sum(Rainfall_fraction[which(d18O_all >= -2 & d18O_all < 0)], na.rm=T),
sum(Rainfall_fraction[c(which(d18O_all >= -4 & d18O_all < -2))], na.rm=T),
sum(Rainfall_fraction[c(which(d18O_all >= -6 & d18O_all < -4))], na.rm=T),
sum(Rainfall_fraction[c(which(d18O_all >= -8 & d18O_all < -6))], na.rm=T),
sum(Rainfall_fraction[c(which(d18O_all >= -10 & d18O_all < -8))], na.rm=T),
sum(Rainfall_fraction[c(which(d18O_all >= -12 & d18O_all < -10))], na.rm=T),
sum(Rainfall_fraction[c(which(d18O_all >= -14 & d18O_all < -12))], na.rm=T),
sum(Rainfall_fraction[which(d18O_all < -14)], na.rm=T))

isotope_group = c(1,-1,-3,-5,-7,-9,-11,-13,-15)

precip_amount_number = floor(rain_amt_group*500)
grt_0 = kk[which (kk[,1] >0),]
btw_0_2 = kk[which (kk[,1] <= 0 & kk[,1] > -2),]
btw_2_4 = kk[which (kk[,1] <= -2 & kk[,1] > -4),]
btw_4_6 = kk[which (kk[,1] <= -4 & kk[,1] > -6),]
btw_6_8 = kk[which (kk[,1] <= -6 & kk[,1] > -8),]
btw_8_10 = kk[which (kk[,1] <= -8 & kk[,1] > -10),]
btw_10_12 = kk[which (kk[,1] <= -10 & kk[,1] > -12),]
btw_12_14 = kk[which (kk[,1] <= -12 & kk[,1] > -14),]
less_14 = kk[which (kk[,1] <= -14),]

jj = rbind(grt_0[sample(nrow(grt_0), precip_amount_number[1]), ],
btw_0_2[sample(nrow(btw_0_2), precip_amount_number[2]), ],
btw_2_4[sample(nrow(btw_2_4), precip_amount_number[3]), ],
btw_4_6[sample(nrow(btw_4_6), precip_amount_number[4]), ],
btw_6_8[sample(nrow(btw_6_8), precip_amount_number[5]), ],
btw_8_10[sample(nrow(btw_8_10), precip_amount_number[6]), ],
btw_10_12[sample(nrow(btw_10_12), precip_amount_number[7]), ],
btw_12_14[sample(nrow(btw_12_14), precip_amount_number[8]), ],
less_14[sample(nrow(less_14), precip_amount_number[9]), ])

##############
btw_2_8 = kk[which (kk[,1] <= -2 & kk[,1] > -8),]
btw_8_12 = kk[which (kk[,1] <= -8 & kk[,1] > -12),]

jj1 = rbind(grt_0[sample(nrow(grt_0), precip_amount_number[1]), ],
btw_0_2[sample(nrow(btw_0_2), precip_amount_number[2]), ],
btw_2_8[sample(nrow(btw_2_8), sum(precip_amount_number[3],precip_amount_number[4],precip_amount_number[5])), ],
#btw_4_6[sample(nrow(btw_4_6), precip_amount_number[4]), ],
#btw_6_8[sample(nrow(btw_6_8), precip_amount_number[5]), ],
btw_8_12[sample(nrow(btw_8_12), sum(precip_amount_number[6],precip_amount_number[7])), ],
#btw_10_12[sample(nrow(btw_10_12), precip_amount_number[7]), ],
btw_12_14[sample(nrow(btw_12_14), precip_amount_number[8]), ],
less_14[sample(nrow(less_14), precip_amount_number[9]), ])
plot(density(jj1[,1]))
```

```{r}
barplot(rev(rain_amt_group*100),main = "Rainfall proportion by isotope",
xlab = "Precipitation d18O",
ylab = "Percentage rainfall",
names.arg = c("<-15","-13","-11","-9","-7","-5", "-3","-1" , ">0"),
col = "darkred",
horiz = F)


########plot amouut weighted bivariate distribution
h_precip_mean1 = mean(d2H_all[aa], na.rm=T)
o_precip_mean1 = mean(d18O_all[aa], na.rm=T)

var_hydro1 = var(d2H_all[aa], na.rm = T)
var_oxy1 = var(d18O_all[aa], na.rm=T)
c_oh1 = cov(d2H_all[aa], d18O_all[aa])
kk1 = rmvnorm(10000, c(o_precip_mean1,h_precip_mean1), matrix(c(var_oxy1, rep(c_oh1,2), var_hydro1),2,2))
#plot(kk1[,1], kk1[,2])
#abline(10,8)
#grid()
```

```{r}
#########Plot density
bivn.kde1 <- kde2d(kk1[,1], kk1[,2], n = 500)
image(bivn.kde1,  xlim = c(-17,4), ylim = c(-130,30), xlab = "d18O", ylab = "d2H")
#points(kk[,1], kk[,2], alpha = 0.8 )
grid()
contour(bivn.kde1, add = TRUE, lwd = 0.5)
abline(LMWL_Bengal$coefficients[1],LMWL_Bengal$coefficients[2], lwd = 1, lty= 2, col = "blue")
title("unweighted precip isotope distri")
#######
```


### Importing the surface water data

We have only kept the isotope data with depth

```{r}
SW_isotope <- read.csv('SW_isotopes.csv', as.is = T)
SW_Bengal = data.frame(cbind(SW_isotope$Sample_ID, SW_isotope$Country, SW_isotope$Study_ID, 
                             SW_isotope$Water_Source , SW_isotope$Depth_m,
                             SW_isotope$d18O, SW_isotope$d2H, SW_isotope$Long, SW_isotope$Lat))
colnames(SW_Bengal) = c("Sample_ID", "Country", "Study_ID", "Water_Source","Depth_m", "d18O","d2H", "Long", "Lat")
```

<br/>

### Surface water data

```{r}
isotope_bengal_sw = data.frame(rbind(SW_Bengal,iso_Beng_sw))
isotope_bengal_sw = subset(isotope_bengal_sw, isotope_bengal_sw$d2H != "NA")
isotope_bengal_sw = subset(isotope_bengal_sw, isotope_bengal_sw$d18O != "NA")
isotope_bengal_sw$d18O = as.numeric(as.character(isotope_bengal_sw$d18O))
isotope_bengal_sw$d2H = as.numeric(as.character(isotope_bengal_sw$d2H))
isotope_bengal_sw$Depth_m = as.numeric(as.character(isotope_bengal_sw$Depth_m))
isotope_bengal_sw$Dex = isotope_bengal_sw$d2H - 8*isotope_bengal_sw$d18O

riv = isotope_bengal_sw %>%
  filter(d18O < -7.5 & d2H >-60 & d2H < -50)    

surfw = isotope_bengal_sw %>%
  filter(d18O > -7.5)   

surfw = isotope_bengal_sw 

LEL_Bengal = lm(surfw$d2H ~surfw$d18O)
LEL_Bengal_low = predict(LEL_Bengal, interval = "prediction")[,2]

#surf_lower = lm(LEL_Bengal_low~surfw$d18O)

var_oxy_sw = var(surfw$d18O, na.rm =T)
var_hydro_sw = var(surfw$d2H, na.rm =T)
c_oh_sw = cov(surfw$d18O[-which(is.na(surfw$d2H))], surfw$d2H[-which(is.na(surfw$d2H))])
h_sw_mean = mean(surfw$d2H,na.rm=T) 
o_sw_mean = mean(surfw$d18O) 


```

### Importing the groundwater data

```{r include=F}
Sas_UKan_GW <- read.csv('sashidharan_2013_UKansas_final_GW.csv', as.is = T)
Chak_EES_GW <- read.csv('Chakravorty_EES_2009_GW.csv', as.is =T,fileEncoding="latin1")
Stuben_AG_GW <- read.csv('Stuben_2003_AG_Malda_GW.csv', as.is =T)
Bibhash_GW <- read.csv('Bibhash_Jessore_WB_isotopes_GW.csv',as.is =T)
Mcarthur_2016_GW <-read.csv('Mcarthur_2016_EST_GW.csv', as.is = T)
##Ghosal_GW <-read.csv('Ghosal_2014_GW.csv', as.is = T) ##NO ISOTOPE DATA
Desbarats_GW <-read.csv('Desbarats_2014_2017_GW.csv', as.is = T)
Stute_GW <-read.csv('Stutue_WRR_2007_GW.csv', as.is = T)
Sengupta_GW <-read.csv('Sengupta_ESandT_2008_GW.csv', as.is = T)
Datta_GW <-read.csv('Datta_JGR_2011_GW.csv', as.is = T)
```

<br/>

### Subseting only the isotope data 

This is done to make this data comparable to the data obtained from the database

```{r include=FALSE}
Sas_UKan_GW= data.frame(cbind(Sas_UKan_GW$Sample_ID, Sas_UKan_GW$Country, Sas_UKan_GW$Study_ID, Sas_UKan_GW$Water_Source, Sas_UKan_GW$Depth_m,Sas_UKan_GW$d18O, Sas_UKan_GW$d2H, Sas_UKan_GW$Long, Sas_UKan_GW$Long))
colnames(Sas_UKan_GW) = c("Sample_ID", "Country", "Study_ID", "Water_Source","Depth_m", "d18O","d2H","Long", "Lat")

sapply(Sas_UKan_GW, class)

Chak_GW= data.frame(cbind(Chak_EES_GW$Sample_ID, Chak_EES_GW$Country, Chak_EES_GW$Study_ID, Chak_EES_GW$Water_Source, Chak_EES_GW$Depth_m, Chak_EES_GW$d18O, Chak_EES_GW$d2H, Chak_EES_GW$Long, Chak_EES_GW$Lat))
colnames(Chak_GW) = c("Sample_ID", "Country", "Study_ID", "Water_Source","Depth_m", "d18O","d2H","Long", "Lat")



Stuben_GW= data.frame(cbind(Stuben_AG_GW$Sample_ID, Stuben_AG_GW$Country, Stuben_AG_GW$Study_ID, Stuben_AG_GW$Water_Source, 
                            Stuben_AG_GW$Depth_m,Stuben_AG_GW$d18O, Stuben_AG_GW$d2H, Stuben_AG_GW$Long, Stuben_AG_GW$Lat))
colnames(Stuben_GW) = c("Sample_ID", "Country", "Study_ID", "Water_Source","Depth_m", "d18O","d2H","Long", "Lat")



Bibhash_GW= data.frame(cbind(Bibhash_GW$Sample_ID, Bibhash_GW$Country, Bibhash_GW$Study_ID, Bibhash_GW$Water_Source, 
                             Bibhash_GW$Depth_m, Bibhash_GW$d18O, Bibhash_GW$d2H, Bibhash_GW$Long, Bibhash_GW$Lat))
colnames(Bibhash_GW) = c("Sample_ID", "Country", "Study_ID", "Water_Source","Depth_m", "d18O","d2H","Long", "Lat")

Mcarthur_2016_GW = data.frame(cbind(Mcarthur_2016_GW$Sample_ID, Mcarthur_2016_GW$Country, Mcarthur_2016_GW$Study_ID, Mcarthur_2016_GW $Water_Source, 
                                    Mcarthur_2016_GW $Depth_m, Mcarthur_2016_GW $d18O, Mcarthur_2016_GW $d2H, Mcarthur_2016_GW$Long, Mcarthur_2016_GW$Lat))
colnames(Mcarthur_2016_GW ) = c("Sample_ID", "Country", "Study_ID", "Water_Source","Depth_m", "d18O","d2H","Long", "Lat")

Desbarats_GW = data.frame(cbind(Desbarats_GW $Sample_ID, Desbarats_GW$Country, Desbarats_GW$Study_ID, Desbarats_GW$Water_Source, Desbarats_GW$Depth_m, Desbarats_GW$d18O, Desbarats_GW$d2H, Desbarats_GW$Long, Desbarats_GW$Lat))
colnames(Desbarats_GW) = c("Sample_ID", "Country", "Study_ID", "Water_Source","Depth_m", "d18O","d2H","Long", "Lat")

Stute_GW = data.frame(cbind(Stute_GW $Sample_ID, Stute_GW$Country, Stute_GW$Study_ID, Stute_GW$Water_Source, 
                            Stute_GW$Depth_m, Stute_GW$d18O, Stute_GW$d2H, Stute_GW$Long, Stute_GW$Lat))
colnames(Stute_GW) = c("Sample_ID", "Country", "Study_ID", "Water_Source","Depth_m", "d18O","d2H","Long", "Lat")


Sengupta_GW = data.frame(cbind(Sengupta_GW $Sample_ID, Sengupta_GW$Country, Sengupta_GW$Study_ID, Sengupta_GW$Water_Source, 
                               Sengupta_GW$Depth_m, Sengupta_GW$d18O, Sengupta_GW$d2H, Sengupta_GW$Long, Sengupta_GW$Lat))
colnames(Sengupta_GW) = c("Sample_ID", "Country", "Study_ID", "Water_Source","Depth_m", "d18O","d2H", "Long", "Lat")


Datta_GW = data.frame(cbind(Datta_GW $Sample_ID, Datta_GW$Country, Datta_GW$Study_ID, Datta_GW$Water_Source, 
                            Datta_GW$Depth_m, Datta_GW$d18O, Datta_GW$d2H, Datta_GW$Long, Datta_GW$Lat))
colnames(Datta_GW) = c("Sample_ID", "Country", "Study_ID", "Water_Source","Depth_m", "d18O","d2H","Long", "Lat")
```


<br/>

## We will combine the database data with non-database data

### Groundwater data

```{r include=F}
isotope_bengal_gw = data.frame((rbind(Datta_GW,Sengupta_GW, Stute_GW, Desbarats_GW ,Mcarthur_2016_GW,
                                      Bibhash_GW, Stute_GW, Stuben_GW, Chak_GW, Sas_UKan_GW)))
isotope_bengal_gw$d18O <- as.numeric(levels(isotope_bengal_gw$d18O))[isotope_bengal_gw$d18O]
isotope_bengal_gw$d2H <- as.numeric(levels(isotope_bengal_gw$d2H))[isotope_bengal_gw$d2H]
isotope_bengal_gw$Long <- as.numeric(levels(isotope_bengal_gw$Long))[isotope_bengal_gw$Lat]
isotope_bengal_gw$Lat <- as.numeric(levels(isotope_bengal_gw$Lat))[isotope_bengal_gw$Lat]



sapply(isotope_bengal_gw, class)

isotope_bengal_gw = data.frame((rbind(isotope_bengal_gw,iso_Beng_gw)))
isotope_bengal_gw$Depth_m <- as.numeric(levels(isotope_bengal_gw$Depth_m))[isotope_bengal_gw$Depth_m]

sapply(isotope_bengal_gw, class)

isotope_bengal_gw$Dex = isotope_bengal_gw$d2H - 8*isotope_bengal_gw$d18O
which(isotope_bengal_gw$Dex < -20)
isotope_bengal_gw = isotope_bengal_gw[-2805,]
```


<br/>

```{r echo = F}
gw_d18O <- isotope_bengal_gw[order(isotope_bengal_gw$Depth_m),]
rem = which(is.na(gw_d18O$d18O))
gw_d18O = gw_d18O[-rem,]
rem1 = which(is.na(gw_d18O$Depth_m))
gw_d18O = gw_d18O[-rem1,] 
gw_d18O = gw_d18O[order(gw_d18O$Depth_m),]
```


<br/>

### let's divide the data in 3 groups

```{r}
shallow = gw_d18O %>% 
  filter(Depth_m <50)

inter = gw_d18O %>% 
  filter(Depth_m>50 & Depth_m <150)

deep = gw_d18O %>% 
  filter(Depth_m>150)

deep1 = gw_d18O %>% 
  filter(Depth_m>150 & Study_ID != "VanGeen_bangladesh_deep_wells_2015")


lex = gw_d18O %>% 
  filter(Depth_m>150 & Study_ID == "VanGeen_bangladesh_deep_wells_2015")

lex = lex[sample(nrow(lex), 70), ]

iso_gw = rbind(shallow,inter,deep1,lex)
rem_h = which(is.na(iso_gw$d2H))
iso_gw = iso_gw[-rem_h,]
#iso_gw_deep = deep_isotope1 


#######get repeat isotope values out

iso_gw_rem_duplicates = iso_gw[,c(5,6,7,10)]
iso_gw = iso_gw[-which(duplicated(iso_gw_rem_duplicates)),]
```
 
 
<br/>

### calculations

```{r}

oxy_gw = iso_gw[c(1:nrow(iso_gw) ),6]
hydro_gw = iso_gw[c(1:nrow(iso_gw)),7]

rem_data = c(which(hydro_gw - 8.1*oxy_gw - 10.2 >= 0),which(hydro_gw - 8.1*oxy_gw -10.2 <= -10.2))

hydro_rem_mix_model = hydro_gw[rem_data]
hydro_mix_model = hydro_gw[-rem_data]
oxy_rem_mix_model = oxy_gw[rem_data]
oxy_mix_model = oxy_gw[-rem_data]

mean_precip_prior_dist <-vector()
mean_river_prior_dist <-vector()
mean_surf_prior_dist <-vector()
mean_precip_prior_raw <-vector()
mean_river_prior_raw <-vector()
mean_surf_prior_raw <-vector()
mean_precip_sol <-vector()
mean_river_sol <-vector()
mean_surf_sol <-vector()
raw_surf <-vector()
raw_river <-vector()
raw_precip <-vector()
dist_precip_gw <-vector()
dist_river_gw <-vector()
dist_surf_gw <-vector()

#########Lets calculate the prior
prior_surf <-vector()
prior_river <-vector()
prior_precip <-vector()
Avg_surf <-vector()
  Avg_river <-vector()
Avg_precip <-vector()
precip_a <-vector()
 river_a <-vector()
surf_a <-vector()
```


#### calculate the distance between groundwater sample and the endmembers
```{r}
for (k in 1: nrow(oxy_mix_model)){
oxy_river = -8
hydro_river = oxy_river*(as.numeric(LMWL_Bengal$coefficients[2])) +as.numeric(LMWL_Bengal$coefficients[1])
dist_precip_gw[k] = abs(8* oxy_mix_model[k] - hydro_mix_model[k]  + 10.2)/(65^0.5)
dist_river_gw[k] = (((oxy_mix_model[k] - oxy_river)^2 + (hydro_mix_model[k] - hydro_river)^2))^0.5
dist_surf_gw[k] = abs(5.6* oxy_mix_model[k] - hydro_mix_model[k]  -7.6)/((5.6*5.6 +1)^0.5)
prior_surf[k] = 1/dist_surf_gw[k]/(1/dist_surf_gw[k] + 1/dist_river_gw[k]+ 1/dist_precip_gw[k])
prior_river[k] = 1/dist_river_gw[k]/(1/dist_surf_gw[k] + 1/dist_river_gw[k]+ 1/dist_precip_gw[k])
prior_precip[k] = 1/dist_precip_gw[k]/(1/dist_surf_gw[k] + 1/dist_river_gw[k]+ 1/dist_precip_gw[k])

}
```


### plot prior calculations for the model
```{r}
##################plot prior############
library(viridis)
library(gridExtra)
library(RColorBrewer)
precip =  ggplot()+ geom_point(aes(x=oxy_mix_model,y=hydro_mix_model, fill = prior_precip), shape  = 21, size = 2.5) +
  geom_point(aes(x=-8,y=-54.5), shape  = 22, size = 4, color = "purple", stroke = 2)+
  geom_abline(intercept = as.numeric(LMWL_Bengal$coefficients[1]), 
              slope = as.numeric(LMWL_Bengal$coefficients[2]), color="black", linetype="solid", size=0.5)+
    geom_abline(intercept = as.numeric(LEL_Bengal$coefficients[1]), 
              slope = as.numeric(LEL_Bengal$coefficients[2]), color="red", linetype="dashed", size=0.5)+
  scale_fill_viridis(option = "D")+  scale_x_continuous(name="18O",limits=c(-8, -1)) +
  scale_y_continuous(name="2H", limits=c(-55, -5)) + theme_bw() +
theme(legend.position = "none") +  ggtitle("Prior - Precipitation")

river =  ggplot()+ geom_point(aes(x=oxy_mix_model,y=hydro_mix_model, fill = prior_river), shape  = 21, size = 2.5) +
  geom_point(aes(x=-8,y=-54.5), shape  = 22, size = 4, color = "purple", stroke = 2)+
  geom_abline(intercept = as.numeric(LMWL_Bengal$coefficients[1]), 
              slope = as.numeric(LMWL_Bengal$coefficients[2]), color="black", linetype="solid", size=0.5)+
    geom_abline(intercept = as.numeric(LEL_Bengal$coefficients[1]), 
              slope = as.numeric(LEL_Bengal$coefficients[2]), color="red", linetype="dashed", size=0.5)+
  scale_fill_viridis(option = "D")+  scale_x_continuous(name="18O",limits=c(-8, -1)) +
  scale_y_continuous(name="2H", limits=c(-55, -5)) + theme_bw() +
theme(legend.position = "none") +  ggtitle("Prior - River")

surf =  ggplot()+ geom_point(aes(x=oxy_mix_model,y=hydro_mix_model, fill = prior_surf), shape  = 21, size = 2.5) +
  geom_point(aes(x=-8,y=-54.5), shape  = 22, size = 4, color = "purple", stroke = 2)+
  geom_abline(intercept = as.numeric(LMWL_Bengal$coefficients[1]), 
              slope = as.numeric(LMWL_Bengal$coefficients[2]), color="black", linetype="solid", size=0.5)+
    geom_abline(intercept = as.numeric(LEL_Bengal$coefficients[1]), 
              slope = as.numeric(LEL_Bengal$coefficients[2]), color="red", linetype="dashed", size=0.5)+
  scale_fill_viridis(option = "D")+  scale_x_continuous(name="18O",limits=c(-8, -1)) +
  scale_y_continuous(name="2H", limits=c(-55, -5)) + theme_bw() +  theme(legend.position = c(0.9, 0.3))+
  ggtitle("Prior - Standing water")
  
grid.arrange(precip, river, surf, nrow=2)

```

### which surface samples could be used for a given groundwater sample
```{r}
#########################################number of possible surface water sources for each sample
surf_end <- vector()
for(i in 1:length(oxy_mix_model)){
  surf_end[i] =  length(unique(c(which((hydro_mix_model[i] -isotope_bengal_sw$d2H)/(oxy_mix_model[i] - isotope_bengal_sw$d18O) > 8.1),which(oxy_mix_model[i] <= isotope_bengal_sw$d18O & hydro_mix_model[i] <= isotope_bengal_sw$d2H))))
}
```

```{r}
####################
#######################calcuation of mixing model
#################
ddd =1
  n = 496*ddd
mat_row = length(oxy_mix_model)
#mat_row = 100
mat_col=nrow(isotope_bengal_sw)
mat_col = 356
isotope_all_oxy= array(NA, c(mat_col,n,mat_row))
isotope_all_hydro= array(NA, c(mat_col,n,mat_row))
isotope_used = array(NA, c( mat_col,n,mat_row))
source_used = array(NA,  c( mat_col,n,mat_row))
source_input = array(NA,  c( mat_col,n,mat_row))

isotope_oxy_used = array(NA, c(mat_col,n,mat_row))
 source_oxy_used = array(NA, c(mat_col,n,mat_row))
 isotope_hydro_used = array(NA, c(mat_col,n,mat_row))
 source_hydro_used = array(NA, c(mat_col,n,mat_row))
contri_surf = array(NA, c(mat_col,n,mat_row))
 contri_precip = array(NA, c(mat_col,n,mat_row))

for (k in 1: mat_row){

oxy_river = -8
hydro_river = oxy_river*(as.numeric(LMWL_Bengal$coefficients[2])) +as.numeric(LMWL_Bengal$coefficients[1])

###### distance between sample and river, surface and precipitation
dist_precip_gw[k] = abs(8* oxy_mix_model[k] - hydro_mix_model[k]  + 10.2)/(65^0.5)
dist_river_gw[k] = (((oxy_mix_model[k] - oxy_river)^2 + (hydro_mix_model[k] - hydro_river)^2))^0.5
dist_surf_gw[k] = abs(5.6* oxy_mix_model[k] - hydro_mix_model[k]  -7.6)/((5.6*5.6 +1)^0.5)
prior_surf[k] = 1/dist_surf_gw[k]/(1/dist_surf_gw[k] + 1/dist_river_gw[k]+ 1/dist_precip_gw[k])
prior_river[k] = 1/dist_river_gw[k]/(1/dist_surf_gw[k] + 1/dist_river_gw[k]+ 1/dist_precip_gw[k])
prior_precip[k] = 1/dist_precip_gw[k]/(1/dist_surf_gw[k] + 1/dist_river_gw[k]+ 1/dist_precip_gw[k])


#######################

bbb <- matrix(NA, ncol = mat_col, nrow = mat_row)
dist <- matrix(NA, ncol = mat_col, nrow = mat_row)


surf_source = matrix(NA, ncol = n, nrow = mat_col)
river_source = matrix(NA, ncol = n, nrow = mat_col)
precip_source = matrix(NA, ncol = n, nrow = mat_col)
bbb <- matrix(NA, ncol = n, nrow = mat_col)
dist_surf= vector()

dist_precip = matrix(NA, ncol = n, nrow = mat_col)

#######################start j loop

for (j in 1:mat_col){
  print(k)
  print(j)
  
oxy_surf = isotope_bengal_sw$d18O[j]
hydro_surf = isotope_bengal_sw$d2H[j]

c <-vector()
f_precip <- vector()
f_river <-vector()
f_surf <- vector()
num <- vector()
dem <- vector()
A_prs <-vector()
A_gps <-vector()
A_grp <-vector()
A_grs <-vector()


jj1 = rbind(grt_0[sample(nrow(grt_0), precip_amount_number[1]*ddd), ],
btw_0_2[sample(nrow(btw_0_2), precip_amount_number[2]*ddd), ],
btw_2_8[sample(nrow(btw_2_8), sum(precip_amount_number[3],precip_amount_number[4],precip_amount_number[5])*ddd), ],
btw_8_12[sample(nrow(btw_8_12), sum(precip_amount_number[6],precip_amount_number[7])*ddd), ],
btw_12_14[sample(nrow(btw_12_14), precip_amount_number[8]*ddd), ],
less_14[sample(nrow(less_14), precip_amount_number[9]*ddd), ])

  oxy_precip = jj1[,1]
  hydro_precip = jj1[,2]
###############start i loop

  for(i in 1:n){
    
  
A_prs[i] = abs(0.5*(oxy_precip[i]*(hydro_river - hydro_surf) + oxy_river*(hydro_surf - hydro_precip[i]) + oxy_surf*(hydro_precip[i] - hydro_river)))

A_grs[i] = abs(0.5*(oxy_mix_model[k]*(hydro_river - hydro_surf) + oxy_river*(hydro_surf - hydro_mix_model[k]) + oxy_surf*(hydro_mix_model[k]- hydro_river)))

A_grp[i] = abs(0.5*(oxy_mix_model[k]*(hydro_river - hydro_precip[i]) + oxy_river*(hydro_precip[i] - hydro_mix_model[k]) + oxy_precip[i]*(hydro_mix_model[k]- hydro_river)))

A_gps[i] = abs(0.5*(oxy_mix_model[k]*(hydro_surf - hydro_precip[i]) + oxy_surf*(hydro_precip[i] - hydro_mix_model[k]) + oxy_precip[i]*(hydro_mix_model[k]- hydro_surf)))


if (abs(A_prs[i] - (A_gps[i]  + A_grp[i] +A_grs[i])) == 0){
  
  num[i] = ((hydro_surf - hydro_precip[i])*(oxy_mix_model[k] - oxy_precip[i]) - (oxy_surf -oxy_precip[i])*(hydro_mix_model[k]- hydro_precip[i]))
  dem[i] = ((hydro_precip[i] - hydro_river)*(oxy_surf - oxy_precip[i]) - (oxy_precip[i] - oxy_river)*(hydro_surf - hydro_precip[i]))

f_river[i] = num[i]/dem[i]
  
f_precip[i] = (oxy_mix_model[k] - oxy_surf + f_river[i]*(oxy_surf - oxy_river))/(oxy_precip[i] - oxy_surf)
  
f_surf[i] = 1 - f_river[i] - f_precip[i]
} else {
  f_river[i] = -999
  
f_precip[i] = -999
  
f_surf[i] = -999
}
 
surf_source[j,i] = f_surf[i]
precip_source[j,i] = f_precip[i]
river_source[j,i] = f_river[i]
source_input[j,i,k] = oxy_surf
if(surf_source[j,i] >0){
 bbb[j,i] = 1
 isotope_oxy_used[j,i,k] = oxy_precip[i]
 source_oxy_used[j,i,k] = oxy_surf
 isotope_hydro_used[j,i,k] = hydro_precip[i]
 source_hydro_used[j,i,k] = hydro_surf
contri_surf[j,i,k] = f_surf[i]
 contri_precip[j,i,k] = f_precip[i]
}
isotope_all_oxy[j,i,k] = oxy_precip[i]
isotope_all_hydro[j,i,k] = hydro_precip[i]
 }
###end loop i


}
####end loop j

raw_surf[k] = mean(surf_source[which(surf_source>0)]) ####raw mean of surf
raw_river[k] = mean(river_source[which(surf_source>0)])   ####raw mean of river
raw_precip[k] = mean(precip_source[which(surf_source>0)])   ####raw mean of precip

}
########end loop k
```



